Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd
update ggplot

```{r}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
Talk more about it.

>>>>

```{r}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
Talk more about it.
